Automating Verification of MPC Security

### 2023-06-09 popl24/hyperprop.tex
checkpoint

In this section we formulate a new hyperproperty that we show is sound
for passive security in the real/ideal model, called
\emph{noninterference modulo output ($\NIMO$)}. We do not claim
completeness with respect to passive security, but soundness
guarantees that enforcement of $\NIMO$ in our analyses implies passive
security. In Section \section{section-bruteforce} we show how $\NIMO$ can
be automatically enforced in a brute-force manner, and in
Section \section{section-bruteforce}

>>>>

In this section we formulate a new hyperproperty that we show is sound
for passive security in the real/ideal model, called
\emph{noninterference modulo output ($\NIMO$)}. We do not claim
completeness with respect to passive security, but soundness
guarantees that enforcement of $\NIMO$ in our analyses implies passive
security. In Section \ref{section-bruteforce} we show how $\NIMO$ can
be automatically enforced in a brute-force manner, and in
Section \ref{section-composition}
